\LARGE \bf \pyRobots{}, a toolset for robot executive control

### 2014-09-18 paper.tex
Lot of little things, including making sure it fits into 6 pages

temporal planning/temporal constraints: T-REX~\cite{mcgann2007trex} -> sensing-planning-acting

ROAR: ~\cite{degroote2011roar}

@@

Projects like PRS, Golog or {\sc cram} have large scopes:

\pyRobots{} positions itself in this landscape as a lightweight eDSL (in a similar
fashion to {\sc roby} or {\sc teer}), that focuses on high-level behaviours
implementation. It seeks unobtrusive interaction with the other components of
the robot software stack, using Python as ubiquitous binding language. Similar
to {\sc urbi}, it focuses on transparent preemptive concurrency and event-based programming.
Also, \pyRobots{}' model favours hierarchical task composition over plans, and does not
provide by itself any task planning service, delegating this to external tools.

\subsection{Guiding principles}

\begin{itemize}
    \item Use a de-facto standard language (Python) to ease adoption (familiar to
        many researchers, large software ecosystem, excellent integration with
        most robotic softwares, in particular common middlewares like ROS or
        YARP)
    \item should be as lightweight/transparent as possible (in particular from a
        syntax perspective) so that the
        programmer can focus on the programming of the behaviours (I'm
        watching you, SMACH)
    \item should enforce as few design choices as possible. 'convention over
        configuration' as often as possible
\end{itemize}

\subsection{Main features}

Parallelism (all \emph{actions} are asynchronous) and event-based programming
are at the core.

It also offers support for robot resources management (locking of ``parts'' of
the robot) and uniform manipulation of 6D poses (that integrates transparently
with other tools like ROS's {\sc tf} when available).

\section{Concepts and Overview}

@@

\begin{figure}
        \centering
        \includegraphics[width=0.8\columnwidth]{log}
        \caption{Screenshot of \pyRobots{} log analyser, processing the log of the
        experiment presented at section~\ref{croq}}
        \label{log_view}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Detailed Example}
% 
% \begin{listing}[h!]
% 
% \begin{pythoncode}
%     import time
%     from robots import GenericRobot
%     from robots.decorators import action, lock
%     from robots.resources import Resource
%     from robots.signals import ActionCancelled
% 
%     # create a 'lockable' resource for our robot
%     WHEELS = Resource("wheels")
% 
%     class MyRobot(GenericRobot):
% 
%       def __init__(self):
%         super(MyRobot, self).__init__()
% 
%         # create (and set) one element in the robot's state.
%         # Here a sonar.
%         self.state["sonar"] = 10.
% 
%         # do whatever other initialization you need :-)
% 
%       def send_goal(self, pose):
%         # move your robot using your favorite middleware
%         print("Starting to move towards %s" % pose)
% 
%       def stop(self):
%         # stop your robot using your favorite middleware
%         print("Motion stopped")
% 
%       def whatever_lowlevel_method_you_need(self):
%         pass
% 
%     @lock(WHEELS)
%     @action
%     def move_forward(robot):
%       """ Actions are written in a simple imperative, 
%           blocking style.
%       """
% 
%       # the target pose: simply x += 1.0m in the robot's 
%       # frame. pyRobots will handle the frames 
%       # transformations as needed.
%       target = [1.0, 0., 0., "base_link"]
% 
%       try:
%         robot.send_goal(target)
% 
%         while(robot.pose.distance(robot.pose.myself(), 
%                                   target) > 0.1):
%             # robot.sleep is exactly like time.sleep, 
%             # except it lets the pyrobots signals pass 
%             # through.
%             robot.sleep(0.5)
% 
%         print("Motion succeeded")
% 
%       except ActionCancelled:
%         # if the action is cancelled, clean up your state
%         robot.stop()
% 
% 
%     with MyRobot() as robot:
% 
%       # Turn on DEBUG logging.
%       # Shortcut to configure the std Python logging system
%       robot.debug()
% 
%       robot.whenever("sonar", below = 0.3).do(move_forward)
% 
%       try:
%         while True:
%           time.sleep(0.5)
%       except KeyboardInterrupt:
%         pass
% \end{pythoncode}
% \caption{Full example of a \pyRobots{} application.}
% \label{mwe}
% \end{listing}
%

@@

\begin{table}[h]
    \centering
    \begin{tabular}{lll}
        \toprule
        Study                 & Robot & Middleware \\ \midrule
        Roboscopie            & PR2       & ROS, {\sc GenoM} \\
        Interactive Grounding & PR2, LAAS-CNRS's Jido & ROS, {\sc GenoM} \\
        CoWriter              & Nao       & ROS, NAOqi  \\
        Ranger at kindergarten & EPFL's Ranger & ROS, aseba  \\
        \bottomrule
    \end{tabular}
    \caption{Overview of significant experiments and studies where \pyRobots{}
    has been used.}
\end{table}

\subsubsection{Roboscopie} The first complex deployment scenario for \pyRobots{} was
a theatre performance entitled \emph{Roboscopie}~\cite{lemaignan2012roboscopie}.
The toolkit was created out of the need to control a complex robot (a Willow
Garage PR2) in a structured way, as required for a live performance with a
human\footnote{The original \pyRobots{} script used for the performance can be
accessed from~\url{http://www.laas.fr/roboscopie}. Note that this script does
not reflect anymore the toolkit usage.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[ht!]
\begin{center}
\begin{tabular}{p{0.9\columnwidth}}
    \toprule
    {\bf Manipulation} \\
     {\tt attachobject}, {\tt basicgive}, {\tt basictake}, {\tt close\_gripper}, {\tt configure\_grippers}, {\tt grab\_gripper}, {\tt handover}, {\tt hide}, {\tt open\_gripper}, {\tt pick}, {\tt put}, {\tt put\_accessible}, {\tt release\_gripper}, {\tt show}, {\tt take} \\
     \midrule
    {\bf Gaze control} \\
     {\tt glance\_to}, {\tt look\_at}, {\tt sweep}, {\tt switch\_active\_stereo\_pair}, {\tt track}, {\tt cancel\_track} \\
     \midrule
    {\bf Navigation} \\
     {\tt carry}, {\tt follow}, {\tt cancel\_follow}, {\tt goto}, {\tt moveclose}, {\tt waypoints} \\
     \midrule
    {\bf Local navigation} \\
     {\tt dock}, {\tt rotate}, {\tt translate} \\
     \midrule
    {\bf Posture configuration} \\
     {\tt extractpose}, {\tt idle}, {\tt manipose}, {\tt movearm}, {\tt rest}, {\tt setpose}, {\tt settorso}, {\tt tuckedpose} \\
     \bottomrule
\end{tabular}
\end{center}
\caption{Examples of \pyRobots{} actions (extracted from experiments involving
the PR2 robot).}

>>>>

The T-REX architecture~\cite{mcgann2007trex} partitions the execution control
problem into several agents, each one composed of a (temporal) planner and an
execution layer. At run-time, the different agents are constantly synchronised
to maintain the consistency of the global plan. ROAR~\cite{degroote2011roar}
augments this idea with a logic mechanism allowing the system to automatically
select and start agents depending on the task at hand.

@@

\pyRobots{} positions itself in this landscape as a lightweight eDSL (in a
similar fashion to {\sc roby} or {\sc teer}), that focuses on high-level
behaviours implementation. It seeks unobtrusive interaction with the other
components of the robot software stack, using Python as ubiquitous binding
language. Similar to {\sc urbi}, it focuses on transparent pre-emptive
concurrency and event-based programming.  Also, \pyRobots{}' model favours
hierarchical task composition over plans, and does not provide by itself any
task planning service, delegating this to optional external tools.

%\subsection{Guiding principles}
%
%\begin{itemize}
%    \item Use a de-facto standard language (Python) to ease adoption (familiar to
%        many researchers, large software ecosystem, excellent integration with
%        most robotic softwares, in particular common middlewares like ROS or
%        YARP)
%    \item should be as lightweight/transparent as possible (in particular from a
%        syntax perspective) so that the
%        programmer can focus on the programming of the behaviours (I'm
%        watching you, SMACH)
%    \item should enforce as few design choices as possible. 'convention over
%        configuration' as often as possible
%\end{itemize}
%
%\subsection{Main features}
%
%Parallelism (all \emph{actions} are asynchronous) and event-based programming
%are at the core.
%
%It also offers support for robot resources management (locking of ``parts'' of
%the robot) and uniform manipulation of 6D poses (that integrates transparently
%with other tools like ROS's {\sc tf} when available).
%
\section{Concepts and Overview}

@@

\begin{figure}
        \centering
        \includegraphics[width=0.9\columnwidth]{log}
        \caption{Screenshot of \pyRobots{} log analyser, processing the log of the
        experiment presented at section~\ref{croq}}
        \label{log_view}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{table}[h]
    \centering
    \begin{tabular}{lll}
        \toprule
        Study                 & Robot & Middlewares \\ \midrule
        Roboscopie            & PR2       & ROS, {\sc GenoM} \\
        Interactive Grounding & PR2, LAAS-CNRS's Jido & ROS, {\sc GenoM} \\
        CoWriter              & Nao       & ROS, NAOqi  \\
        Ranger at kindergarten & EPFL's Ranger & ROS, aseba  \\
        \bottomrule
    \end{tabular}
    \caption{Overview of significant experiments and studies where \pyRobots{}
    has been used.}
\end{table}

\subsubsection{Roboscopie} The first complex deployment scenario for \pyRobots{} was
a theatre performance entitled \emph{Roboscopie}~\cite{lemaignan2012roboscopie}.
The toolkit was created out of the need to control a complex robot (a Willow
Garage PR2) in a structured way, as required for a live performance with a
human\footnote{The original \pyRobots{} script used for the performance can be
accessed from~\url{http://www.laas.fr/roboscopie}. Note that this script does
not reflect anymore the current toolkit usage.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[ht!]
\begin{center}
\begin{tabular}{p{0.9\columnwidth}}
    \toprule
    {\bf Manipulation} \\
     {\tt attachobject}, {\tt basicgive}, {\tt basictake}, {\tt close\_gripper}, {\tt configure\_grippers}, {\tt grab\_gripper}, {\tt handover}, {\tt hide}, {\tt open\_gripper}, {\tt pick}, {\tt put}, {\tt put\_accessible}, {\tt release\_gripper}, {\tt show}, {\tt take} \\
     \midrule
    {\bf Gaze control} \\
     {\tt glance\_to}, {\tt look\_at}, {\tt sweep}, {\tt switch\_active\_stereo\_pair}, {\tt track}, {\tt cancel\_track} \\
     \midrule
    {\bf Navigation} \\
     {\tt carry}, {\tt follow}, {\tt cancel\_follow}, {\tt goto}, {\tt moveclose}, {\tt waypoints} \\
     \midrule
    {\bf Local navigation} \\
     {\tt dock}, {\tt rotate}, {\tt translate} \\
     \midrule
    {\bf Posture configuration} \\
     {\tt extractpose}, {\tt idle}, {\tt manipose}, {\tt movearm}, {\tt rest}, {\tt setpose}, {\tt settorso}, {\tt tuckedpose} \\
     \bottomrule
\end{tabular}
\end{center}
\caption{Examples of \pyRobots{} actions.}
